---
author: "Admin"
date: "24 4 2019"
output:
  html_document:
    df_print: paged
    includes:
      after_body: footer.html
runtime: shiny
params:
  data: ""
  data_to_predict: NULL
  title: ""
  target: ""
  type: ""
---

<style type="text/css">
h1.title, h4.date, h4.abstract, p.abstract{
  text-align: center;
}
h1.title{
  margin-top: 30px;
}
h4.abstract{
  margin-top: 50px;
}
.outer{
width: 100%;
}
.scrolltable { margin-top: 20px; height: 450px; overflow: auto; }
.scrolltable table { border-collapse: collapse; }
.scrolltable tr:nth-child(even) { background: #EEE; }
.expand tr:nth-child(even) { background: #EEE; }
#expandButton{
  cursor: pointer;
}
#pipeline{
  background-color: #EEE;
  font-size: 110%;
  padding-bottom: 0px;
  padding-top: 0px;
  border-color: transparent;
  width: fit-content;
}
.generations{
  text-align: center;
}
.predictions div{
  text-align: center;
 }
.explanation{
  text-align: center;
 }
.predictions div{
  max-height: 300px;
  margin-top: 15px;
  padding: 0px !important;
}
.predictions div table thead tr th{
  text-align: center !important;
}
.predictions div table tbody tr td{
  text-align: center !important;
}
.explanationLime .content div{
  max-height: 300px;
  margin-top: 15px;
  padding: 0px !important;
}
.explanationLime .content table thead tr th{
  text-align: center !important;
}
.explanationLime .content table tbody tr td{
  text-align: center !important;
}
.explanationLime img{
  display: block;
  margin: 0 auto;
}
.explanationLimeTestData img{
  display: block;
  margin: 0 auto;
}
.exexpand{
  display: block;
}
.excollapse{
  display: none;
}
.collapsible {
  background-color: #eee;
  color: #444;
  cursor: pointer;
  padding: 18px;
  width: 100%;
  border: none;
  outline: none;
  font-size: 15px;
  text-align: center;
}
</style>

<script>
var isExpanded = false;
var isExpanded2 = false;
function expand() {
  if (document.getElementById('section-scrolltable') != null){
  isExpanded ? document.getElementById('section-scrolltable').setAttribute("class", "scrolltable") : document.getElementById('section-scrolltable').setAttribute("class", "expand")
  isExpanded = !isExpanded}
  else{isExpanded ? document.getElementById('scrolltable').setAttribute("class", "scrolltable") : document.getElementById('scrolltable').setAttribute("class", "expand")
  isExpanded = !isExpanded}
}
function expand2(){
  if (document.getElementById('section-explanationSample') != null){
    isExpanded2 ? document.getElementById('section-explanationSample').setAttribute("class", "excollapse") :     document.getElementById('section-explanationSample').setAttribute("class", "exexpand")
    isExpanded2 = !isExpanded2}
    else{isExpanded2 ? document.getElementById('explanationSample').setAttribute("class", "excollapse") :     document.getElementById('explanationSample').setAttribute("class", "exexpand")
    isExpanded2 = !isExpanded2}
}
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("summarytools")
require("tpotr")
require("mlr")
require("stringr")
require("knitr")
require("iml")
require("lime")
require("ggplot2")
require("kableExtra")
require("magrittr")
require("dplyr")
```

<!-- HEADER SECTION --> 
<div class="container outer">

<div class="row">

<div class="col-sm">

<h1 class="title">`r paste('Automatic report for the dataset:',params$title)`</h1>
<h4 class="date">`r Sys.Date()`</h4>
<h4 class="abstract">Abstract</h4>
<p class="abstract"> This report analyses the dataset `r params$title`. </p>
<hr>

</div>

</div>

</div>

<!-- FIRST SECTION --> 

<div class="container outer">

<div class="row">

<div class="col-sm">

<h3>Brief description of the data set</h3>
<p> The dataset analyzed in this report is described hereafter. The passed dataset has `r ncol(params$data)` features (columns) and `r nrow(params$data)` observations (rows). The feature of interest, the target column, is "`r params$target`" and has `r length(levels(params$data[,params$target]))` classes (`r levels(data[,params$target])`). The following table summarizes all features of the data set and provides a descriptive overview of the individual features. It provides the following information: <strong>No:</strong> The number of the feature indicating the order in which it appears in the dataset. <strong>Variable:</strong> The name of the feature and its class. <strong>Stats/Values:</strong> An insight into the feature's values. <strong>Freqs: </strong> The frequency, proportions or number of distinct values. <strong>Graph:</strong> A histogram or barplot of the feature's values. <strong> Valid/Missing:</strong> The number and proportion of valid and missing values in the feature. You can <a id = "expandButton" onclick="expand()">expand/collapse</a> the table.</p><br>

<div id="scrolltable" class="scrolltable">

```{r results='asis', echo=FALSE}
data <- data
print(dfSummary(data, plain.ascii = FALSE, style = "grid", graph.magnif = 0.8, headings = FALSE, tmp.img.dir = "/tmp"))
#dfSummary(data, plain.ascii = FALSE, style = "grid")
```

</div>

</div>

</div>

</div>

<!-- SECOND SECTION --> 

<div class="container outer">

<div class="row">

<div class="col-sm">

<h3>Fitting a machine learning pipeline</h3>

```{r echo=FALSE, include=FALSE}
if(type=="classif"){
  task <- makeClassifTask(data = params$data, target = params$target)
  learner <- makeLearner(cl = "classif.tpot", predict.type = "prob", 
                       population_size = 10, generations = 15, 
                       verbosity = 2)
} else{
  task <- makeRegrTask(data = params$data, target = params$target)
  learner <- makeLearner(cl = "regr.tpot", predict.type = "response", 
                       population_size = 10, generations = 15, 
                       verbosity = 2)
}
mod = NULL; pred = NULL; again = TRUE;
while(again == TRUE){
  result = try({
    mod = train(learner, task)
    # don't uncomment this line or you will not find out as to whether a loop is necessary!!
    pred = predict(obj = mod, newdata = test)
  }, silent = TRUE)
  if (inherits(result, "try-error")){
    again = TRUE
  } else {
    again = FALSE
  }
}
pipeline <- getPipeline(mod)
generations <- getGenerations(mod)
```

<p>The Automated Statistician has fitted a machine learning pipeline, that can predict the target variable "`r params$target`" in the dataset "`r params$title`" with an accurancy of `r max(generations)`. The best machine learning pipeline is:</p>

<pre id="pipeline">
<code>
`r pipeline`
</code>
</pre>

<p>
To fit a machine learning pipeline, the Automated Statistician tried different combination of pipeline operators over `r length(generations)` generations. The best pipeline is the one with the highest accurancy for the input training data. The plot below shows how the accuracy increased during the fitting of the pipeline.
</p>

<div class="generations">
```{r echo=FALSE}
plot(generations, type="b", xlab="Generations", ylab="CV score", xaxt="n")
axis(1, at = seq(1, 15, by = 1), las=2)
```
</div>

<div class="predictions">

`r if(nrow(params$data_to_predict)){"For the provided test data the pipeline predicted the missing target feature values:"}`
```{r echo=FALSE}
if(nrow(params$data_to_predict) > 0){
  test <- params$data_to_predict[, !names(params$data_to_predict) %in% c(params$target)]
  prediction <- cbind("Prediction" = predict(obj = mod, newdata = test)$data$response, test)
  write.csv2(prediction, "./prediction.csv")
  readLines("./prediction.csv") %>% 
  paste0(collapse="\n") %>% 
  openssl::base64_encode() -> encoded
}
```
```{r echo=FALSE, results='asis'}
if(nrow(params$data_to_predict) > 0){
  cat(kable(cbind("i" = as.numeric(rownames(prediction)), prediction)) %>% kable_styling(fixed_thead = TRUE) %>% scroll_box(width = "100%"))
  cat('\n')
  #print(performance(pred = prediction, measures=list(acc)))
}
```
```{r echo=FALSE}
if(nrow(params$data_to_predict) > 0){
  link <- paste0("<a download='prediction.csv' href=", sprintf('data:text/csv;base64,%s', encoded), ">Download this data as   .csv</a>")
}
```
</div>

`r if(nrow(params$data_to_predict)){link}`

</div>

</div>

</div>

<!-- THIRD SECTION --> 

<div class="container outer">

<div class="row">

<div class="col-sm">

<h3>Model explanation</h3>
<p> To explain the fitted machine learning model different model-agnostic methods are used in the following. They are based on the book <i>Interpratable Machine Learning</i> by Christoph Molnar.</p>

```{r include=FALSE}
predictor <- Predictor$new(mod, data = params$data, y = params$target)
imp <- FeatureImp$new(predictor, loss = "ce", compare = "difference")
imp.df <- imp$results
imp.df[,"cum_importance"] <- cumsum(imp.df$importance)
imp.sum <- sum(imp.df$importance)
imp.cum <- imp.df[,"cum_importance"]
imp.df[,"cum_importance"] <- sapply(imp.cum, function(x){
  x / imp.sum
})
min <- min(which(imp.df[,"cum_importance"] > 0.8))
imp.features <- imp.df[1:min,"feature"]
imp.features
```

<br>

<h4>Feature Importance</h4>
<p>To assess the quality of the fitted machine learning model first the importance of each features for the prediction is shown.</p>

<p><i>The importance of a feature is measured by calculating the increase in the model’s prediction error after permuting the feature. A feature is important if shuffling its values increases the model error, because in this case the model relied on the feature for the prediction.</i></p>

<p>The following plot shows the importance of each feature. The ratio of classification error is calculated as follows: Increase in classification error through permutation divided by the original classification error. The dot is the median and the bar describes the range of the classification error ratio.</p>

<div class="explanation">
```{r echo=FALSE}
imp.dat = imp$results
p <- ggplot(data = imp.dat, aes(x=feature, y=importance)) + geom_point()
p + labs(x = "Feature Importance (Classification Error as Loss)", y = "Feature") + theme_bw()
```
</div>

<p>The plot shows that from the <b>`r length(data) - 1`</b> features of the data set the following <b>`r length(imp.features)`</b> are identified as the most important features that account for at least <b>80%</b> of the total prediction error: <b>`r paste(imp.features, sep = ", ")`</b>.</p>

<br>

<h4>Accumulated Local Effects</h4>
<p>The goal of the first step was to analyse which features influence the prediction of the fitted model the most. As a next step it is analyzed, how the features influence the prediction of the model. This is done by accumulated local affects.</p>

<p><i>Accumulated local effects (ALE) describe how features influence the prediction of a machine learning model on average.</i></p>

<p>The following two ALE-plots show how the two most important features <b>(`r paste(imp.features[1:2], sep = ", ")`)</b> influence the prediction of the model:</p>

<div class="explanation">
```{r echo=FALSE}
# Extract feature and produce plot --------------------------------------------
first.feature <- imp.features[1]
ale <- FeatureEffect$new(predictor, feature = first.feature)
ale$plot() + theme_bw()

# Extract result --------------------------------------------------------------
ale.result <- ale$results
temp.result <- ale.result %>%
  group_by_(first.feature) %>%
  slice(which.max(.ale))
temp.result2 <- temp.result %>%
  group_by(.class) %>%
  summarise(min = min(!!sym(first.feature)), max = max(!!sym(first.feature)))

# Extract description ---------------------------------------------------------
levels <- temp.result2[[1]]
ale.desc <- vector(mode="character", length=length(levels))
for(i in 1:length(levels)){
  level <- levels[i]
  temp.result <- subset(temp.result2, .class == level)
  ale.desc[i] <- paste("The class ", "<b>", level, "</b>", " is based on the feature ", 
                       "<b>", first.feature, "</b>", " most likely for values between ",
                       temp.result[[1,"min"]], " and ", paste0(temp.result[[1,"max"]], ". "))
}
```
</div>

<p>For the given classification problem the most important feature according to the feature importance analysis  is <b>`r paste(imp.features[1], sep = ", ")`</b>. The ALE-plot provides an analysis how this feature influences the target <b>`r target`</b> with its `r length(levels)` classes. `r paste(ale.desc, collapse="")`</p>

<div class="explanation">
```{r echo=FALSE}
# Extract feature and produce plot --------------------------------------------
second.feature <- imp.features[2]
ale <- FeatureEffect$new(predictor, feature = second.feature)
ale$plot() + theme_bw()

# Extract result --------------------------------------------------------------
ale.result <- ale$results
temp.result <- ale.result %>%
  group_by_(second.feature) %>%
  slice(which.max(.ale))
temp.result2 <- temp.result %>%
  group_by(.class) %>%
  summarise(min = min(!!sym(second.feature)), max = max(!!sym(second.feature)))

# Extract description ---------------------------------------------------------
levels <- temp.result2[[1]]
ale.desc <- vector(mode="character", length=length(levels))
for(i in 1:length(levels)){
  level <- levels[i]
  temp.result <- subset(temp.result2, .class == level)
  ale.desc[i] <- paste("The class ", "<b>", level, "</b>", " is based on the feature ", 
                       "<b>", second.feature, "</b>", " most likely for values between ",
                       temp.result[[1,"min"]], " and ", paste0(temp.result[[1,"max"]], ". "))
}
```
</div>

<p>The second most important feature according to the feature importance analysis is <b>`r paste(imp.features[2], sep = ", ")`</b>. The plot illustrates how <b>`r paste(imp.features[2], sep = ", ")`</b> influences the target <b>`r target`</b>. `r paste(ale.desc, collapse="")`</p>

<br>

<h4>Lime</h4>
<p>The last step focuses on individual observation to explain why the model makes a certain classification in a given case. This is especially useful when explaining the reason for individual predictions on the predicted data.</p>

<p><i>Local surrogate models like LIME are interpretable models that are used to explain individual predictions of black box machine learning models.</i></p>

<div class="explanationLimeTestData">
<h5>Explaining the predicted values</h5>
<p>For the predicted data Lime provides the explanations below. The colour represents the feature weight and gives an indication, which features and feature values are most responsible for the prediction.</p>
```{r echo=FALSE, results='asis'}
full_predicted_data <- params$data[, !names(params$data) %in% c(params$target)]
full_predicted_data[,params$target] <- predict(obj = mod, newdata = params$data)$data$response
explainer1 <- lime(params$data, mod)
explanation <- lime::explain(test, explainer1, n_labels = 1, n_features = 5)
print(plot_explanations(explanation))
```
</div>

<button class="collapsible" onclick="expand2()">+See more/less observations explained</button>

<div id="explanationSample" class="excollapse">
<p>To explain the inner working of the fitted model even further, 5 observations are randomely selected for each class and their belonging to each class is explained with LIME.</p>

<p>In the following plots for each class 5 selected observations are eplained by LIME.</p>
```{r echo=FALSE, results='asis'}
levels <- levels(full_predicted_data[,params$target])
for(level in levels){
   cat('<div class="explanationLime">')
   cat(paste('<h5> ', level , '</h5>', sep = ""))
   cat('<div class="content">')
   tempdata <- full_predicted_data[full_predicted_data[,params$target] == level,]
   nrow <- nrow(tempdata)
   sample <- sample.int(nrow, size = 5, replace = FALSE)
   tempdata2 <- tempdata[sample,]
   explanation <- lime::explain(tempdata2[, !names(tempdata2) %in% c(params$target)], explainer1, n_labels = 1, n_features = 5)
   for (r in rownames(tempdata2)){
      case <- (explanation %>% filter(case == r))
      #print(case[,c(2,3,10,11)])
      max_weight <- (case %>% filter(feature_weight == max(feature_weight)))
      #print(max_weight[,c(2,3,10,11)])
      tempdata2[r,"Most responsible"] <- max_weight$feature_desc
      tempdata2[r,"Weight"] <- max_weight$feature_weight
      #print(max_weight$feature_desc)
   }
   cat(kable(tempdata2)%>% kable_styling(fixed_thead = TRUE) %>% scroll_box(width = "100%"))
   cat('\n')
   print(plot_explanations(explanation))
   cat('</div>')
   cat('</div>')
}
```

</div>

</div>

</div>

</div>

